The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-05-04 paper/ms.tex
Add sentence on link between FIRE and Sgr
Update orbits table headings

\begin{deluxetable*}{cccccccc}
\tablecaption{Description and names of the three orbits considered in this
work. For the last two columns: $z_{\text{max}}$ is the maximum height of the
orbit while $A_R$ is the magnitude of the radial excursions of the orbit,
computed as one half the maximum radius minus the minimum
radius.\label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} &
\colhead{$A_R$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{kpc}$}}
\startdata 
thin-disk & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 0.12 & 1.29 \\
thick-disk & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.5 & -1520 & 23.0 & 0.85 & 1.19 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 190)$ & 32.8 & -1520 & 529.1 & 6.16 & 2.34
\enddata
\end{deluxetable*}

@@

In the upper panels, we see that the midplane is
relatively flat in the inner galaxy, but additional encounters drive strong
midplane variation. In the lower left panel, we see a strong $m=2$ mode develop,
consistent with the $R=8\,\kpc$ panel of Figure~17 in
\citet{2018MNRAS.481..286L}.

>>>>

\begin{deluxetable*}{cccccccc}
\tablecaption{Description and names of the three orbits considered in this
work. For the last two columns: $z_{\text{max}}$ is the maximum height of the
orbit while $\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$ is the magnitude of the radial excursions of the orbit. In the epicyclic approximation, $A_z = z_{\text{max}}$ and $A_R = \frac{1}{2}(R_{\text{max}} - R_{\text{min}})$ \label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} &
\colhead{$\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{kpc}$}}
\startdata 
thin-disk & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 0.12 & 1.29 \\
thick-disk & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.5 & -1520 & 23.0 & 0.85 & 1.19 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 190)$ & 32.8 & -1520 & 529.1 & 6.16 & 2.34
\enddata
\end{deluxetable*}

@@

In the upper panels, we see that the midplane is
relatively flat in the inner galaxy, but additional encounters drive strong
midplane variation. In the lower left panel, we see a strong $m=2$ mode develop,
consistent with the $R=8\,\kpc$ panel of Figure~17 in
\citet{2018MNRAS.481..286L}. The lower right panel, which shows the galaxy after some relaxation has occured is qualitatively similar to the midplane variations we saw in the FIRE simulations (Figure~\ref{fig:midplane}), evidence that they are at least partially driven by mergers.
